\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{epsfig}
\usepackage{enumerate}
\usepackage{float}
\usepackage{listings}
\frenchspacing
\linespread{1.2}                                          %espacio entre líneas
\setlength{\parskip}{1.5ex plus 0.2ex minus 0.2ex}        %espacio entre párrafos
\setlength{\columnsep}{0.9cm}                 %espacio entre columnas
\usepackage{indentfirst}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{url}
\usepackage{multicol}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{moreverb}
\usepackage{hyperref}
\usepackage{caption}

\newcommand\R{R}
\newenvironment{keywords}{\begin{description}\item[Keywords:]}{\end{description}}

%\center{\emph{Desarrollo de una plataforma astroinformática para la administración y análisis inteligente de datos a gran escala} \\}

\title{
\center{\textbf{Presence of the Virtual Observatory in the World} \\}
\author{
        Mauricio Solar, Marcelo Mendoza, Jonathan Antognini, José Marroquín, \\
        Jorge Ibsen, Lars Nyman,
        Eduardo Vera, Diego Mardones, Guillermo Cabrera,\\
        Paola Arellano,
        Karim Pichara, Nelson Padilla,
        Ricardo Contreras, \\ Neil Nagar,
        Victor Parada.
}
\date{Valparaíso, \today}
}

\begin{document}
\maketitle

\begin{center}
    \begin{abstract}
		This document publicizes the virtual observatories projects that make
up the International Virtual Observatory Alliance (IVOA), how they are
distributed worldwide and trough some brief descriptions, the tools which they
themselves develop under standards that facilitate the sharing of astronomical
knowledge and the interoperability. For this research were reviewed the website
of the IVOA and its membership, scientific publications, articles in book and
other electronics sources. This document is required by an initiative which
intends from Chile to development of an astro-informatics platform to manage
and analyse large-scale data based on the IVOA standards, project which
involves the active participation of university students of the Federico Santa
Mar\'{i}a Technical University.
    \end{abstract}
\end{center}

\vspace{0.4cm}

\begin{center}
\begin{keywords}
    IVOA, ChiVO, VO.
\end{keywords}
\end{center}
\newpage

\input{include/introduction}
\newpage

\input{include/vo_distribution}
\newpage

\input{include/vo_list}
\newpage

\input{include/conclusions}
\newpage
 
\section{References}
Hanisch, R., \& Quinn, P. (n.d.) The International Virtual Observatory.
Retrieved from \url{http://www.ivoa.net/about/TheIVOA.pdf}\\

Borne, K. (n.d.) Virtual Observatories, Data Mining, and Astroinformatics. In
H.E. Bond (Ed.), \textit{Planets, Stars and Stellar Systems} (pp. 409-443).
Vol. 2. Dordrecht: Springer Science$ + $Business Media.\\

Anonymous. (2013, April 17). Proyecto Fondef: Innovador proyecto de la USM
proveer\'{a} a la Red de Telescopios ALMA de un sofisticado observatorio
virtual. Retrieved from
\url{http://www.conicyt.cl/fondef/2013/04/17/proyecto-fondef-innovador-proyecto-de-la-usm-proveera-a-la-red-de-telescopios-alma-de-un-sofisticado-observatorio-virtual/}\\

Foncea, V. (2013, April 12). Observatorios Virtuales: Desarrollo chileno de
astroinform\'{a}tica para ALMA. Retrieved from
\url{http://www.almaobservatory.org/es/anuncios-eventos/542-virtual-observatories-chilean-development-of-astronomical-computing-for-alma}\\

De Young, D. (2010, October). A Vision for the US Virtual Astronomical
Observatory. Retrieved from
\url{http://www.usvao.org/documents/VAOVisionDocumentOct2010c.pdf}\\

		Quinn, P., \& G\'{o}rsky, K.(2002). The Canadian Virtual Observatory
Project. In \textit{Toward an International Virtual Observatory}. Retrieved
from \url{http://link.springer.com/chapter/10.1007%2F10857598_4#page-1}\\

Ishihara, Y., Mizumoto, Y., Ohishi, M., Kawaray, K. (2004, September 8).
Construction of Japanese Virtual Observatory (JVO). Retrieved from
\url{http://www.fujitsu.com/downloads/MAG/vol40-2/paper05.pdf}\\
\end{document}
