\section{List of IVOA Virtual Observatories}
\subsection{America}
\subsubsection{Brazilian Virtual Observatory (BRAVO)}
The BRAVO \cite{website:bravo-home} was born with the Declarations of Intentions
signed on 18th of August, 2008 by six research institutes and the Brazilian
Astronomical Society (SBA, in its Portuguese acronym). Later, the Brazilian
Virtual Observatory was founded by the National Institute for Science and
Technology in Astrophysics (INCT-A, in its Portugese acronym).

\begin{itemize}
\item \textbf{Projects}
\begin{itemize}
\item BRAVO@IAG
\item BRAVO@INPE
\begin{itemize}
\item \textbf{Description\footnote{On the \textbf{List of IVOA Virtual
Observatories} section, a brief description of each proyect appears only if was
found some information of them in the sources.}:} generate investment in
information technology on Computational Infraestructure, Data Grid, Data
Processing and Data Mining.
\end{itemize}
\item BRAVO@LNA
\begin{itemize}
\item \textbf{Description:} making of a virtual observatory dedicated to
Southern Astrophysical Research Telescope (SOAR) data from Brazilian
astronomers.  
\end{itemize}
\item BRAVO@UFSC
\begin{itemize}
\item \textbf{Description:} researching of the of the power spectral synthesis
as a mean to estimate the physical properties of the galaxies.
\end{itemize}
\item CYCLOPS
\begin{itemize}
\item \textbf{Description:} a software that models the optical emission from AM
Her systems including the four Stokes parameters.
\end{itemize}
\end{itemize}
\end{itemize}

\subsubsection{Canadian Virtual Observatory (CVO)}
The CVO \cite{website:cvo-home} \nocite{SchadeDowlerDurand2004} is a project
within the Canadian Astronomy Data Centre.

\begin{itemize}
\item \textbf{Projects}
\begin{itemize}
\item Data Sharing (VOSpace 2.0)
\begin{itemize}
\item \textbf{Description:} a service that allows to share files and collaborate
with team members.
\end{itemize}
\item Table Access Protocol (TAP-1.0)
\begin{itemize}
\item \textbf{Description:} a service that allows the access to all the data
described by the Common Archive Observation Model (CAOM) in use at the CADC and
tables from other projects.
\end{itemize}
\item Observation Model Core Components (ObsCore-1.0)
\begin{itemize}
\item \textbf{Description:} a model that implements a standard view for
\textbf{Table Access Protocol (TAP-1.0)}.
\end{itemize}
\item Simple Image Access (SIA-1.0)
\begin{itemize}
\item \textbf{Description:} a SIA-1.0 compliant query service for easy access to
calibrated images from most our data collections.
\end{itemize}
\end{itemize}
\end{itemize}

\subsubsection{Nuevo Observatorio Virtual Argentino (NOVA)}
The NOVA \cite{website:nova-home} was founded by eight institutions\footnote{The
institutions that founded the NOVA are the Observatorio Astron\'{o}mico de
C\'{o}rdova (OAC), the Facultad de Ciencias Astron\'{o}micas y Geof\'{i}sicas de
La Plata/Universidad de Nacional de la Plata (FCAGLP/UNLP), the Instituto de
Astrof\'{i}sica de La Plata (IALP), the Instituto Argentino de
Radioastronom\'{i}a (IAR), the Instituto de Astronom\'{i}a y F\'{i}sica del
Espacio (IAFE), the Instituto de Ciencias Astron\'{o}micas, de la Tierra y del
Espacio (ICAFE), the Instituto de Astronom\'{i}a Te\'{o}rica y Experimental
(IATE), and the Complejo Astron\'{o}mico El Leoncito (CASLEO).} among which
important astronomical institutes and the National University of La Plata
through the Faculty of Astronomical Sciences and Geophysics of La Plata. It was
born in January 2009.  From June 2013, the NOVA will begin its operations and
intends, in addition to provide the astronomical observations from its official
website, to implement a platform web where it can work with the
data\footnote{Agencia CTyS. (2013, May 9). Instituciones astron\'{o}micas lanzan
el Nuevo Observatorio Virtual Argentino. \textit{Agencia CTyS}. Retrieved from:
\url{http://www.ctys.com.ar/index.php?idPage=20&idArticulo=2585}}.

\begin{itemize}
\item \textbf{Projects}
\begin{itemize}
\item NOVA@CASLEO
\item NOVA@IAFE
\begin{itemize}
\item \textbf{Description:} building a database for the
observations\footnote{The more than 6 terabytes of date was stored in CDs and
DVDs.} reached by the H-Alpha Solar Telescope for Argentina (HASTA) solar
telescope and its applications.
\end{itemize}
\item NOVA@IALP
\item NOVA@IAR
\item NOVA@IATE
\item NOVA@ICATE
\begin{itemize}
\item \textbf{Description:} building a database for the spectroscopic
observations\footnote{Until 1987, the database was stored in photographic
plates. After that year, the information was stored in CDs and DVDs.} available
at ICATE.
\end{itemize}
\item NOVA@OAC
\item NOVA@FCAGLP
\end{itemize}
\end{itemize}

\subsubsection{US Virtual Astronomical Observatory (VAO)}
The VAO \cite{website:vao-home} \nocite{DeYoung2010} is the succesor of the NVO
(National Virtual Observatory) and was founded by the NSF and the NASA. It is in
charge of the VAO, LLC, an entity created by the Associated Universities, Inc.
(AUI) and the Association of Universities for Research in Astronomy (AURA). VAO
advise the VAO Science Council
\footnote{\url{http://www.usvao.org/governance/}}. The US VO is a co-founder of
the IVOA.

\begin{itemize}
\item \textbf{Projects}
\begin{itemize}
\item Data Discovery Tool
\begin{itemize}
\item \textbf{Description:} a web tool that allows to find datasets from
astronomical collections known to the VO like the Hubble Space Telescope (HST),
the Chandra X-ray Observatory, the Spitzer Space Telescope, among other.
\end{itemize}
\item Iris: SED Analysis Tool
\begin{itemize}
\item \textbf{Description:} a downloadable application for the finding, plotting
and fitting the Spectral Energies Distributions (SEDs). 
\end{itemize}
\item Time Series Search Tool
\begin{itemize}
\item \textbf{Description:} a web tool that allows to access the time series
data sets at the Harvard Time Series Center (TSC), the NASA Exoplanet Archive
and the Catalina Real-Time Transient Survey, and analize them with the
periodogram application of the NASA Exoplanet Archive.
\end{itemize}
\item Cross-Comparision Tool
\begin{itemize}
\item \textbf{Description:} a web tool that performs croos-comparisons between
one table supplied by the user and other of an online source catalog, for a
user-specified match radius. This returns the all sources in the online catalog
that are within the radius.
\end{itemize}
\end{itemize}
\end{itemize}

\subsection{Europe}
\subsubsection{Armenian Virtual Observatory (ArVO)}
The ArVo \cite{website:arvo-home} is based on the Digital First Byurakan Survey
(DFBS), a project between Byurakan Astrophysical Observatory, Armenia; ``La
Sapienza'' Universit\`{a} di Roma, Italia; Cornell University, USA and
VO-France\footnote{Mickaelian, A., Sargsyan, L., Gigoyan, K., Erastova, L.,
Sinamyan, P., Hovhannisyan, L., ...Mykayelyan, G. (2007, December). Science with
the Armenian Virtual Observatory (ArVo).  Retrieved from
\url{http://www.grid.am/pdf/Science_with_the_Armenian_Virtual_Observatory_(ArVO).pdf}}.
Its virtual observatory was launched in February 2008\footnote{Armenian
News-NEWS.am. (2012, February 18). Armenia creates virtual observatory server.
\textit{NEWS.am}. Retrieved from \url{http://news.am/eng/news/93843.html}}.

\begin{itemize}
\item \textbf{Projects}
\begin{itemize}
\item ``Search for new interesting objects of definite types by low-dispersion
template spectra'' 
\begin{itemize}
\item \textbf{Description:} ``modeling of spectra [...] [for a] QSOs, Seyfert
galaxies, white dwarfs, [...] late-type stars (K-M, S, carbon)'' 
\end{itemize}
\end{itemize}
\begin{itemize}
\item ``Optical identifications of new gamma, X-ray, IR and radio sources''
\begin{itemize}
\item \textbf{Description:} using the Byurakan 2.6 [m] telescope, ``the first
test resulted in 145 objects found, 81 being known QSOs/Sys, and 64 new
candidates (including 23 NVSS and FIRST radio sources)''.
\end{itemize}
\end{itemize}
\begin{itemize}
\item ``Identification of the newly found IR sources from Spitzer Space
Telescope (SST)''
\begin{itemize}
\item \textbf{Description:} ``73 unidentified sources in the Bootes region have
been found and clasified on the DFBS plates''\footnote{Mickaelian, A. (2006,
August). Science projects with the Armenian Virtual Observatory (Arvo). Karel A.
van der Hucht (Ed.), \textit{Highlights of Astronomy} (p. 529). Vol. 14. Prague:
Cambridge University
Press. }.
\end{itemize}
\end{itemize}
\end{itemize}

\subsubsection{Hungarian Virtual Observatory \cite{website:hvo-home} (HVO)}

\begin{itemize}
\item \textbf{Projects}
\begin{itemize}
\item Spectrum Service for VO
\begin{itemize}
\item \textbf{Description:} a proposal that intends to add several features and
make two substantial improvements\footnote{Does not specified what several
features and the two substantial improvements.} to the web services that
contains spectra of galaxies and the other astronomical objects. 
\end{itemize}
\item Synthetic Spectrum Service
\begin{itemize}
\item \textbf{Description:} a proposal that intends to serve, as a web service,
the ready made spectra for the users.
\end{itemize}
\item Photometric Redshift Estimation
\begin{itemize}
\item \textbf{Description:} a proposal that intends to execute as a web service
a method developed by themselves that is capable to estimate redshift from
photometry increasing by two orders of magnitude the objects number of known
distance. 
\end{itemize}
\item Linking WebServices to GRID clusters
\begin{itemize}
\item \textbf{Description:} a proposal that intends, among other, to improvement
the operating systems inter communication, because there are simulations
optimized for differents SOs and the rewritten of the codes for one different in
some cases results a inaccessible task.
\end{itemize}
\item Information Bulletin on Variable Stars
\begin{itemize}
\item \textbf{Description:} a bulletin on benhalf of the Commission
27\footnote{http://www.konkoly.hu/IAUC27/} and
42\footnote{http://www.konkoly.hu/IAUC42/} of the International Astronomical
Union (IAU), published by the Konkoly Observatory of the Hungarian Academy of
Sciences. 
\end{itemize}
\item Debrecen Photoheliographic Data (DPD)
\begin{itemize}
\item \textbf{Description:} a sunspot catalogue with the heliographic positions
and the areas of sunspots. A continuation of Greenwich Photoheliographic
Results (GPR) that had been discontinued on 1976.
\end{itemize}
\end{itemize}
\end{itemize}

\subsubsection{AstroGrid}
The AstroGrid \cite{website:astrogrid-home} is the United Kingdom's virtual
observatory. It began as a project in 2001 and was launched in April 2008 along
its working service and user software. It has been financed by the Particle
Physics and Astronomy and Research Council (PPARC) and the Science \& Technology
Facilities Council (STFC).

\begin{itemize}
\item \textbf{Projects}
\begin{itemize}
\item Topcat
\begin{itemize}
\item \textbf{Description:} an interactive graphical viewer and editor for
tabular data for formats like the Flexible Image Transport System (FITS) and
VOTable.
\end{itemize}
\item VODesktop
\begin{itemize}
\item \textbf{Description:} an analysis tools wich allows limit the choice of
resources through specific data saving.
\end{itemize}
\item AstroRuntime
\begin{itemize}
\item \textbf{Description:} an API implemented in JAVA wich facilitates the
access to the \textbf{VODesktop} services from almost any programming language
\footnote{On the AstroGrid's official website there is a document about how to
access VODesktop using Python script at
\url{http://www.astrogrid.org/agpython.html}}.
\end{itemize}
\end{itemize}
\end{itemize}

\subsubsection{European Space Agency Virtual Observatory (ESA-VO)}
The ESA-VO \cite{website:esa-vo-home} aims to have the European Space Astronomy
Centre (ESAP) as the VO node for all European astronomy. It is a member of the
European Virtual Observaory (EURO-VO) and with European Southern Observatory
(ESO) co-funded the EURO-VO Facility Centre. It participated of EURO-VO Data
Centre Alliance (EURO-VO DCA) and EURO-VO Astronomical Infraestructure for Data
Access (EuroVO-AIDA), and work with the formal partners of Euro-VO International
Cooperation Empowerment (EuroVO-ICE) and EURO-VO Technology Centre (VOTECH).

\begin{itemize}
\item \textbf{Projects}
\begin{itemize}
\item DALToolKit
\begin{itemize}
\item \textbf{Description:} a downloadable software based on JAVA that allows to
publish in the VO following the Data Access Layer (DAL) protocol. It converts
incoming standard DAL requests into database specific SQL queires, then
serializes the database result into VOTable responses. 
\end{itemize}
\item IVOA Resource Registry
\begin{itemize}
\item \textbf{Description:} the official EURO-VO resource registry under the
name of EURO-VO Full Harvestable VO Resource Registry that 
\end{itemize}
\item VOSpec
\begin{itemize}
\item \textbf{Description:} a multi-wavelength spectral analysis tool with
access to atomic and molecular databases, spectra and theorical models
registered in the VO. It can be downloadable and accessed through Internet.
\end{itemize}
\item Science Activities in the VO
\begin{itemize}
\item \textbf{Description:} development at the European Space Astronomy Centre
(ESAC) of research projects based on VO, tutorial that teachs to use the tools
made by the Science Archives Team (SAT), among other.
\end{itemize}
\end{itemize}
\end{itemize}

\subsubsection{European Virtual Observatory (EURO-VO)}
The EURO-VO \cite{website:euro-vo-home} is the continuation of Astrophysical
Virtual Observatory (AVO). The AVO project conducted was conceived by the
European Commision and six organizations \footnote{The six organizations that
founded the AVO togheter with the European Commision are the European Southern
Observatory (ESO), the European Space Agency (ESA), the AstroGrid, the
CNRS-supported Centre de Données Astronomiques de Strasbourg (CDS), the
University Louis Pasteur; the CNRS-supported TERAPIX astronomical data centre,
the Institut d'Astrophysique; and the Jodrell Bank Observatory, the Victoria
University of Manchester.} to research about the scientific requirements and
technologies necessary to build an Euopean virtual observatory. The ``EURO-VO
aims at deploying and operational VO in
Europe''\footnote{\url{http://www.euro-vo.org/}}.\\

\begin{itemize}
\item \textbf{Projects}
\begin{itemize}
\item VOTECH
\begin{itemize}
\item \textbf{Description:} the first project that implemented the concept of
the EURO-VO Technology Centre (EURO-VOTC) as part of the Euro-VO.
\end{itemize}
\item EURO-VO Data Centre Alliance (EuroVO-DCA)
\begin{itemize}
\item \textbf{Description:} it is supported by the European Union (EU) in the
framework of the FP6 e-Insfraestructure Communication Network Development
initiative (project RI031675). It began on 1st of September, 2006, and ended on
31th of December, 2008.
\end{itemize}
\item EURO-VO Astronomical Infraestructure for Data Access (EuroVO-AIDA)
\begin{itemize}
\item \textbf{Description:} it is supported by the European Union (UE) in the
framework of the FP7 e-Infrastructure Scientific Research Repositories
initiative (project RI2121104). It began on 1st of February, 2008, and ended on
31th of July, 2010.
\end{itemize}
\item Euro-VO International Cooperation Empowerment (EuroVO-ICE)
\begin{itemize}
\item \textbf{Description:} as a Coordination Action supported by the European
Union (UE) in the framework of the FP7 INFRA-2010-2.3.3 Research Infrastructures
initiative (project 261541). It began on 1st of September, 2010 and ended on
31th of August, 2012, and succeed EuroVO-AIDA and the EuroVO-DCA.
\end{itemize}
\item EuroVO-CoSADIE
\begin{itemize}
\item \textbf{Description:} as a Coordination Action supported by the EU in the
framework of the FP7 INFRA-2012-3.3 Research Infraestructure initiative (project
312559). It began on 1st of September, 2012, and will end on 31th of August,
2014.
\end{itemize}
\end{itemize}
\end{itemize}

\subsubsection{German Astrophysical Virtual Observatory (GAVO)}
The GAVO \cite{website:gavo-home} was launched in 2003\footnote{Its first
publications dates from 2003. In 2004, H. Adorf and GAVO Team talking about
``GAVO - after one year'' at the Astronomical Data Analysis (ADA) III Sant'Agata
sui due Golfi, Italy. The birth of this VO is inferred from the above.}. It is
financed through the Federal Ministry of Education and Research (BMBF).

\begin{itemize}
\item \textbf{Projects}
\begin{itemize}
\item GAVO Data Center
\begin{itemize}
\item \textbf{Description:} a growing collection of data and services provided
on behalf of third parties. Some of the GAVO services are also available on
\url{http://dc.zah.uni-heidelberg.de/}
\end{itemize}
\item GAVO Data Center
\begin{itemize}
\item \textbf{Description:} a collection of data and services on behalf of third
parties.
\end{itemize}
\item MPA Simulations access
\begin{itemize}
\item \textbf{Description:} a web service for querying the results of the
Millennium simulation using SQL.
\end{itemize}
\item MultiDark Database
\begin{itemize}
\item \textbf{Description:} a service wich gives access to data from MultiDark
and Bolshoi simulations using SQL queries.  It based on the Millennium Web
Application.
\end{itemize}
\item RAVE archive search
\begin{itemize}
\item \textbf{Description:} an access to a growing archive of radial velocities
for more than 400 000 stars.
\end{itemize}
\item TheoSSA
\begin{itemize}
\item \textbf{Description:} a service for providing spectral energy
distributions based on model atmosphere calculations.
\end{itemize}
\end{itemize}
\end{itemize}

% \subsubsection{Observatoire Virtuel France (VO-France)}
% \begin{itemize}
% \item \textbf{Projects}
% \end{itemize}

\subsubsection{Spanish Virtual Observatory (SVO)}
The SVO \cite{website:svo-home} started in June 2004 and its participants are
the Centro de Astrobiolog\'{i}a (INTA-CSIC), the Artificial Intelligence
Department of the National University of Distance Education (UNED, in its
Spanish acronym), the University of C\'{a}diz and the Center of Scientific and
Academic Services of Catalonia (CESCA, in its Spanish acronym).

\begin{itemize}
\item \textbf{Projects}
\begin{itemize}
\item VO Sed Analyzer (VOSA)
\begin{itemize}
\item \textbf{Description:} a tool that allows to analyze stellar and galactic
data reading user photometry-tables, querying ``several photometrical catalogs
accessible through VO services'', querying ``VO-compliant theorical models
(spectra)'', performing ``a statistical test to determinate which model
reproduced best observed
data''\footnote{\url{http://svo2.cab.inta-csic.es/theory/vosa/helpw.php?action=help2&what=intro&otype=star}},
among other. 
\end{itemize}
\item VOSED
\begin{itemize}
\item \textbf{Description:} a service that builds Spectral Energy Distributions
(SEDs) gathering information from the spectrocopic services in VO. It has two
modes depending of the query objects number.
\end{itemize}
\item TESELA
\begin{itemize}
\item \textbf{Description:} a service that allows to acces the catalog of blank
regions. It is based on the application of the Delaunay triangulation of the
sky.
\end{itemize}
\end{itemize}
\end{itemize}

\subsubsection{Italian Virtual Observatory (VObs.it)}
The VObs.it \cite{website:vobs.it-home} besides being member of IVOA, it is a
member of EURO-VO. It was established and founded by the Italian National
Institute for Astrophysics (INAF) and is coordinated by the Information Systems
Units (SI) of this. 

\begin{itemize}
\item \textbf{Projects}
\begin{itemize}
\item SIAP
\begin{itemize}
\item \textbf{Description:} a web services that provides the public Hubble Space
Telescope/Advanced Camera for Surveys (HST/ACS) Great Observatories Origins Deep
Survey (GOOD) data within the VIMOS\footnote{VIMOS is a \textbf{VI}sible imaging
\textbf{M}ulti-\textbf{O}bject \textbf{S}pectrograph, a spectrograph for the
European Southern Observatory Very Large Telescope array (ESO-VLT).}-VLT Deep
Survey-Chandra Deep Field South (VVDS-CDFS).
\end{itemize}
\item SSAP
\begin{itemize}
\item \textbf{Description:} a web service that allows to access the
VVDS-F02-DEEP spectra.
\end{itemize}
\item CONE SEARCH
\begin{itemize}
\item \textbf{Description:} a web service that allows to query in the VVDS-CDFS
catalog. 
\end{itemize}
\item SKYNODE
\begin{itemize}
\item \textbf{Description:} a web service that allows to query in the VVDS
catalogs. 
\end{itemize}
\end{itemize}
\end{itemize}

\subsubsection{Ukrainian Virtual Observatory (UkrVO)}
The concept of UkrVO \cite{website:ukrvo-home} was developed by a working group
of Ukrainian Astronomical Association (UAA) in 2009-2010. In 2009 June, the 8th
Congress of UAA approved the resolution of creation of a consortium of voluntary
joining where each member had the duty to prepare it records of obsevations in
accordance to the VO concept. 

\begin{comment}
\begin{itemize}
\item \textbf{Projects}
\begin{itemize}
\item Variable Star Calculator
\begin{itemize}
\item \textbf{Description:}
\end{itemize}
\item Database of Golosiiv Plate Archive (DBGPA)
\begin{itemize}
\item \textbf{Description:}
\end{itemize}
\item CoLiTec (CLT)
\begin{itemize}
\item \textbf{Description:}
\end{itemize}
\item Joint Digital Archive (JDA)
\begin{itemize}
\item \textbf{Description:}
\end{itemize}
\item FON Astrographic Catalogue (FONAC)
\begin{itemize}
\item \textbf{Description:}
\end{itemize}
\item Mykolaiv Astronomical Observatory (MykAO) digital archive
\begin{itemize}
\item \textbf{Description:}
\end{itemize}
\item Variable Star Calculator
\begin{itemize}
\item \textbf{Description:}
\end{itemize}
\item Variable Star Calculator
\begin{itemize}
\item \textbf{Description:}
\end{itemize}
\item Variable Star Calculator
\begin{itemize}
\item \textbf{Description:}
\end{itemize}
\item Variable Star Calculator
\begin{itemize}
\item \textbf{Description:}
\end{itemize}
\item Variable Star Calculator
\begin{itemize}
\item \textbf{Description:}
\end{itemize}
\item Variable Star Calculator
\begin{itemize}
\item \textbf{Description:}
\end{itemize}
\end{itemize}
\end{itemize}
\end{comment}

\subsection{Asia}
\subsubsection{Chinese Virtual Observatory (China-VO)}
The China-VO \cite{website:china-vo-home} was initiated in 2002 by the National
Astronomical Observatories, Chinese Academy of Sciences. It has four
partners\footnote{The partners of China-VO are the National Astronomical
Observatories, Chinese Academy of Sciences (NAOC); the TianJin University (TJU),
the Central China Normal University (CCNU), Kunming University of Science and
Technology.} and more of twelve collaborators\footnote{The China-VO's
collaborators are the Computer Network Information Center, the Purple Mountain
Astro Obs, the Shangai Astro Obs, the Yunnan Astro Obs, the Tsinghua University,
the JHU, MSR, Caltech, IUCAA, CDS, ICRAR (Australia), NAOJ (Japan), among
other.}.

\begin{itemize}
\item \textbf{Projects}
\begin{itemize}
\item FITS Manager (FM)
\begin{itemize}
\item \textbf{Description:} a downloadable application, as a collaboration
project between China-V0 and VOI, to manage FITS, VOTable, among other files,
hosted in personal computers \footnote{FITS Manager (FM) is downloadble from
\url{http://fm.china-vo.org/app/fm.zip}.} 
\end{itemize}
\item VO Data Access Service (VO-DAS)
\begin{itemize}
\item \textbf{Description:} a data access framework that allows to query large
volumes of astronomical resources like catalogs, spectrum and images through the
command line, a graphical interface or webpage.
\end{itemize}
\item FITS Header Archiving System (FitHAS)
\begin{itemize}
\item \textbf{Description:} a downloadable tool that allows to view and import
the FITS header files into a database table for single or multiple files. It was
also developed by the IBM Center, Tianjin University (TU) and e-Science
application research center, Computer Network Information Center (CNIC), Chinese
Academy of Sciences (CAS).
\end{itemize}
\item Imaging Processing and analysis tool for China\_VO (VO\_IMPAT)
\begin{itemize}
\item \textbf{Description:} a downloadable imaging processing and analysis tool
developed in JAVA that allows to visualize sky images and access related data
from the Beijing Astronomical Data Center (BADC). 
\end{itemize}
\item WDC-Astronomy Archives and Catalogs
\begin{itemize}
\item \textbf{Description:}
\end{itemize}
\item China-VO Grid Registry Area
\begin{itemize}
\item \textbf{Description:}
\end{itemize}
\item VOTFilter, XSL filter for OpenOffice
\begin{itemize}
\item \textbf{Description:}
\end{itemize}
\item VOTable2XHTML
\begin{itemize}
\item \textbf{Description:} a XSLT stylesheet that can be used to transform
VOTable file into XHTML file.
\end{itemize}
\item SkyMouse
\begin{itemize}
\item \textbf{Description:} a search engine that allows to access astronomical
services like web service and CGI service.
\end{itemize}
\item Astrophysical Integrated Research Environment
\begin{itemize}
\item \textbf{Description:}
\end{itemize}
\item VO Tools Worlwide
\begin{itemize}
\item \textbf{Description:}
\end{itemize}
\item LAMOST Online Collaboration Platform
\begin{itemize}
\item \textbf{Description:}
\end{itemize}
\item Chinese Astronomical Data Center 
\begin{itemize}
\item \textbf{Description:}
\end{itemize}
\item WWT Community Beijing
\begin{itemize}
\item \textbf{Description:}
\end{itemize}
\item Glossary of Astronomical Terms
\begin{itemize}
\item \textbf{Description:}
\end{itemize}
\end{itemize}
\end{itemize}

\subsubsection{Japanese Virtual Observatory (JVO)}
The JVO \cite{website:jvo-home} \nocite{IshiharaMizumotoOhishiKawaray2004} was
implemented by the National Astronomical Observatory of Japan (NAOJ) with
collaboration of Fujitsu for the development of JVO prototype systems. It
started in 2002, its VO data services are interoperated from 2004 and an
analysis system was integrated in 2005 to the JVO prototype\footnote{Shirasaki
Y., Tanaka, M., Kawamoto, S., Honda, S., Ohishi, M., Mizumoto, Y., ...Sakamoto,
M. (2006, April 8) Japanese Virtual Observatory (JVO) as an advanced
astronomical research enviroment. Retrieved from:
\url{http://arxiv.org/pdf/astro-ph/0604593v1.pdf}}.

\begin{itemize}
\item \textbf{Projects}
\begin{itemize}
\item JVO portal service
\begin{itemize}
\item \textbf{Description:} a site as portal to various kind of astronomical
resources from the Subaru Telescope, Sloan Digital Sky and ALMA, among other.
\end{itemize}
\end{itemize}
\end{itemize}

\subsubsection{Russian Virtual Observatory (RVO)}
A reason for the construction of the RVO \cite{website:rvo-home} is that
majority of observatories were south of Ex-Soviet Union. After of desintegration
of Ex-URSS, they were located in the territories outside of
Russia\footnote{\url{http://www.inasan.rssi.ru/eng/rvo/project.html}}.

\begin{itemize}
\item
\textbf{Projects}
\begin{itemize}
\item SYNTHESIS
\begin{itemize}
\item \textbf{Description:} SYNTHESIS group's framework project.
\end{itemize}
\item INFOSEM
\begin{itemize}
\item \textbf{Description:} it aims to ``investigate, prototype and disseminate
methodologies and basic techniques allowing construction of semantically
interoperable information systems based on the pre-existing heterogeneous
information
resources''\footnote{http://synthesis.ipi.ac.ru/synthesis/projects/InfoSem/}.
\end{itemize}
\item SEMIMOD
\begin{itemize}
\item \textbf{Description:} ``Modelling and Management of Semi-Structured Data
for Dynamic [World Wide Web applications]''.
\end{itemize}
\item BIOMED
\begin{itemize}
\item \textbf{Description:} ``Methods and tools for development of subject
mediators of he\-te\-ro\-ge\-neous information collections for distributed
digital libraries''.
\end{itemize}
\item REFINE
\begin{itemize}
\item \textbf{Description:} ``Modeling of compositional specifications intended
for automated proof of correctness of refinement of specifications of
requirements by pre-existing components in course of a compositional development
of information systems''.
\end{itemize}
\item VOINFRA
\begin{itemize}
\item \textbf{Description:} ``Devolopment of principles and fundamentals of the
information interoperability in the infraestructure'' of the RVO.
\end{itemize}
\item MULTISOURCE
\begin{itemize}
\item \textbf{Description:} ``Methods for organization of problems solving over
multiple distributed he\-te\-ro\-ge\-neous information sources''.
\end{itemize}
\item RVOAG
\begin{itemize}
\item \textbf{Description:} a RVO public utility center based on AstroGrid.
\end{itemize}
\item ASTROMEDIA
\begin{itemize}
\item \textbf{Description:} ``Methods and tools for supporting subject mediators
architecture in AstroGrid infrastructure'' for the RVO.
\end{itemize}
\item UNIMOD
\begin{itemize}
\item \textbf{Description:} ``Development and prototyping of experimental system
for constructing the unifying information representation models for
interoperable integrating systems of heterogeneous information sources''.
\end{itemize}
\item SEMID
\begin{itemize}
\item \textbf{Description:} ``Research and development of methods and tools for
semantic identification of specifications of heterogeneous information resources
relevant to a scientific problem and their integration in the specifications of
the problem at the scientific information systems''.
\end{itemize}
\item SubjMed
\begin{itemize}
\item \textbf{Description:} ``Investigation of methods and tools for subject
mediation middleware aimed at problems solving over heterogeneous distributed
information resources''.
\end{itemize}
\item ConcMod
\begin{itemize}
\item \textbf{Description:} ``Development of methods and tools for definition of
scientific subject domains conceptual models and problems solving support based
on mediators subject in the hybrid grid-infrastructure''.
\end{itemize}
\item RuleInt
\begin{itemize}
\item \textbf{Description:} ``Integration of rule-based declarative programs and
knowledge databases and services for scientific problems solving over
heterogeneus distributed information resources''.
\end{itemize}
\item ASTROMEDIA Trial
\begin{itemize}
\item \textbf{Description:} ``Hybrid architecture of AstroGrid and Mediator
Middlewere''.
\end{itemize}
\item Galaxies Search
\begin{itemize}
\item \textbf{Description:} ``Distant Galaxies Search Applying AstroGrid''.
\end{itemize}
\item Star Classification
\begin{itemize}
\item \textbf{Description:} ``Eclipsing-binary Stars Classification applying
Ensembled Weka [algorithm] in
AstroGrid''\footnote{\url{http://synthesis.ipi.ac.ru/synthesis/projects}}.
\end{itemize}
\end{itemize}
\end{itemize}

\subsubsection{Virtual Observatory India (VOI)}
The VOI \cite{website:voi-home} is a collaboration between the Inter University
Center for Astronomy and Astrophysics (IUCAA) and the Persistent Systems Ltd.,
and is supported by the Ministry of Communication and Information Technology,
Government of India.

\begin{itemize}
\item \textbf{Projects}
\begin{itemize}
\item VOIPortal
\begin{itemize}
\item \textbf{Description:} an entry to all VOI web services. Can be browse the
data downloading or through VOIMosaic and PyMorph web applications.
\end{itemize}
\item Mosaic Service
\begin{itemize}
\item \textbf{Description:} a software that allows to make mosaic, with
SWarp\footnote{\url{http://www.astromatic.net/software/swarp}} and
SExtractor\footnote{\url{http://www.astromatic.net/software/sextractor}} and
STIFF, of images retrieved from
SDSS\footnote{\url{http://casjobs.sdss.org/vo/DR7SIAP/SIAP.asmx}},
2MASS\footnote{\url{http://irsa.ipac.caltech.edu/applications/2MASS/IM/}} and
HST\footnote{\url{http://archive.stsci.edu/siap/search.php}} image servers.
\end{itemize}
\item PyMorph Service
\begin{itemize}
\item \textbf{Description:} a software that allows to derive morphological
parameters for galaxy images. Is possible to provide to it the output FITS files
generated by Mosaic Service.
\end{itemize}
\item VOPlot
\begin{itemize}
\item \textbf{Description:} a software tool developed in JAVA that allows to
visualize astronomical data available in VOTable, ASCII and FITS formats.
\end{itemize}
\item VOMegaPlot
\begin{itemize}
\item \textbf{Description:} a software tool developed in JAVA that allows to
visualize astronomical data available in VOTable format. It looks just like
VOPlot. There is a client-server version.
\end{itemize}
\item AstroStat
\begin{itemize}
\item \textbf{Description:} a software tool that allows astronomers to use both
and sophisticated statical routines on large datasets uploaded in VOTable or
ASCII format.
\end{itemize}
\item VOCat
\begin{itemize}
\item \textbf{Description:} a software tool that converts astronomical catalogs
to MySQL databases. 
\end{itemize}
\item VOPlatform
\begin{itemize}
\item \textbf{Description:} a software tool developed in JAVA that allows to
place their frequently used VO tools and datasets with others resourcers like
documents, links, among other.
\end{itemize}
\item VOConvert (ConVOT)
\begin{itemize}
\item \textbf{Description:} a software tool that converts ASCII to VOTable
files, FITS to VOTable and VOTable to ASCII.
\end{itemize}
\item Android Cosmological Calculator
\begin{itemize}
\item \textbf{Description:} an Android aplication that allows to input the
Hubble constant, $ \Omega_{m} $ (matter), $ \Omega_{\lambda} $ (vacuum) and the
redshift($ z $), and returns the current age of the Universe, the co-moving
radial distance and volume and the angular size distance at the specified
redshift, and the luminosity distance.
\end{itemize}
\item Android Name Resolver
\begin{itemize}
\item \textbf{Description:} an Android application that allows to input the name
of celestial object and returns information of this like RA/DEC values,
redshift, proper motion, parallax, among other.
\end{itemize}
\item CSharpFITS Package
\begin{itemize}
\item \textbf{Description:} a C\# .NET port of Tom McGlynn's nom.tam.fits JAVA
package\footnote{\url{http://heasarc.gsfc.nasa.gov/docs/heasarc/fits/java/v0.9/javadoc/}}.
\end{itemize}
\item VOTable JAVA Streaming Writer
\begin{itemize}
\item \textbf{Description:} a software that converts data streams in non-VOTable
format, like ASCII or FITS, to the VOTable format.
\end{itemize}
\item C++ parser for VOTable
\begin{itemize}
\item \textbf{Description:} a C++ library to access VOTable files. It has a
non-streaming and streaming version.
\end{itemize}
\item Fits Manager
\begin{itemize}
\item \textbf{Description:} a web-based tool for viewing, creating, adding
extensions and converting FITS files.
\end{itemize}
\item HCT Data Archive System
\begin{itemize}
\item \textbf{Description:} a web-based system that archives the observational
data generated by the Himalayan Chandra Telescope (HCT), a 2 [m] aperture
optical-infrared telescope manufactured by the EOS Technologies Inc. and
remotely operated via dedicated satellite link.
\end{itemize}
\end{itemize}
\end{itemize}
